Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-19 paper.tex
sieve fixup, closes #162

Even though simulation has long been a vital tool in population genetics,
such collaborative software development has historically been uncommon.
A huge proliferation of tools have been published
(the references here are not exhaustive)
and only a small minority of these are actively developed and
maintained today. The ecosystem is highly fragmented, with numerous different
ways of specifying parameters and representing results, and there are
significant software quality issues at all stages. This is unsurprising, since
the majority of simulation software development is performed by students,
often without formal training in software development.
Although this ``Haldane's sieve'' of software has produced many good tools
and enabled decades of research,
it also represents a missed opportunity to invest as a community
in shared infrastructure and mentorship in good software development practice.

>>>>

Even though simulation has long been a vital tool in population genetics,
such collaborative software development has historically been uncommon.
A huge proliferation of tools have been published
(the references here are not exhaustive)
and only a small minority of these are actively developed and
maintained today. The ecosystem is highly fragmented, with numerous different
ways of specifying parameters and representing results, and there are
significant software quality issues at all stages. This is unsurprising, since
the majority of simulation software development is performed by students,
often without formal training in software development.
The result resembles Haldane's sieve for new mutations:
many new pieces of software stay permanently on a dusty shelf of supplementary materials,
while some of those that prove particularly useful when new (like dominant alleles)
are quickly adopted.
Although this has produced many good tools
and enabled decades of research,
it also represents a missed opportunity to invest as a community
in shared infrastructure and mentorship in good software development practice.
